Something with Objects and Names

### 2019-12-05 papers/ACL2020/acl2020_main.tex
small paragraph on faster rcnn models

% To streamline frequently used terms:
\newcommand{\mn}{ManyNames\xspace}

@@

\appendix

\section{Appendices}
\label{sec:appendix}
Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
Upon acceptance, the appendices come after the references, as shown here.

\paragraph{\LaTeX-specific details:}
Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.

\section{Supplemental Material}
\label{sec:supplemental}
Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.

\end{document}

>>>>

% To streamline frequently used terms:
\newcommand{\mn}{ManyNames\xspace}
\newcommand{\vg}{VisualGenome\xspace}

@@

%\appendix
%
%\section{Appendices}
%\label{sec:appendix}
%Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
%Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
%Upon acceptance, the appendices come after the references, as shown here.
%
%\paragraph{\LaTeX-specific details:}
%Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
%
%
%\section{Supplemental Material}
%\label{sec:supplemental}
%Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
%Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.

\bibliographystyle{acl_natbib}
\bibliography{naming}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "acl2020_main"
%%% End:

### 2019-12-05 papers/ACL2020/experiments.tex
small paragraph on faster rcnn models

>>>>

We test two object detection models that are trained with a different vocabulary:

\begin{itemize}
\item FRCNN--VG1600: we used the code and model of the bottom-up attention model (\textit{Bottom-up} henceforth)  \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} \footnote{\url{https://github.com/peteanderson80/bottom-up-attention}} The model is based on the object detection method Faster R-CNN \cite{fasterrcnn2015}. The authors initialized it with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vg.\footnote{Bottom-up is trained with an additional output over attributes, but we only use the object class prediction layer.}

\item FRCNN--MN442: we retrain Faster R-CNN \cite{fasterrcnn2015} on a smaller vocab. We use \citeauthor{anderson2018updown}'s to preprocess the data set, but restrict the object classes to the 442 entry-level names found in ManyNames. For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{https://github.com/jwyang/faster-rcnn.pytorch}} and initialized it with a pretrained ResNet-101 provided in this implementation.\footnote{ResNet-101 was pretrained with Caffe.}
\end{itemize}

We test a range of object classification models via transfer learning, that are finetuned with different vocabulary/training data:

\begin{itemize}
\item ...
\end{itemize}
